A Method for Analysing Heterogeneous Data with 2D Detection Function Distance Sampling

### 2018-04-23 Draft.tex
demonstration changes

The example code included in section 4, as well as an example of the type of code used to produce the pilot simulation studies mentioned in section 5 can be found here:

\url{https://github.com/penguin-coding/LT2D-work/blob/master/LatexRCode.R}

>>>>

The example code included in section 4, as well as an example of the type of code used to produce the pilot simulation studies mentioned in section 5 can be found here: 
\\
\url{https://github.com/penguin-coding/LT2D-work/blob/master/LatexRCode.R}\\

The LT2D functions code before the project:
\\\url{https://github.com/penguin-coding/LT2D-work/blob/master/2DLTfunctions\%20-\%20Copy.r}\\

The LT2D functions after the project:\\\url{
https://github.com/penguin-coding/LT2D-work/blob/master/LT2D/R/2DLTfunctions.r}\\

The LT2D GoF functions after the project:\\
\url{https://github.com/penguin-coding/LT2D-work/blob/master/LT2D/R/2DLTGoF.R}\\

An example of how to fit different covariate formulas to a real data set:\\
